### 2012-12-19 doc/description.tex
updated addAssociation orm

\subsubsection{Add Association}
$
\Phi_{AddAssociation}(a, d) = \inference{ \exists t_s, t_t \in tables(d) : name(t_s) = name(owningClass(a)) \\ \wedge name(t_t) = reference(a) \\ \wedge \not \exists f \in foreignKeys(t_t) : name(f) = name(a) }{ \rho(a,d)}
$

>>>>

\subsubsection{Add Association}
$
\Phi_{AddAssociation}(a, d) = \begin{cases}
\inference{ \exists t_s, t_t \in tables(d) : name(t_s) = name(owningClass(a)) \\ \wedge name(t_t) = reference(a) \\ \wedge \not \exists f \in foreignKeys(t_t) : name(f) = name(a) }{ \rho(a,d) }
 \end{cases}
$
